Fisheries example integrating FLR

### 2021-07-31 notebook/cran_vignettes/SI3.Rmd
Update the vignettes as necessary with changes mentioned in Issue #64 -- mostly typos, but also some small edits to the code that needed to be clarified

  0. *No explicit density independent or dependent removal*. This option does not cause removal to be *directly* caused in a density independent or dependent way. Nevertheless, removal may still be possible if the argument `consume_surv > 0` (its default value is 0). In this case, survival of a resource in a time step depends on that resource consuming at least `consume_surv` in yield on the landscape. In such cases, a natural carrying capacity will be generated as more resources result in higher total consumption. The amount yield that a resource consumes is further affected by both `times_feeding` (how many times the resource moves and feeds on a new landscape cell during a time step) and `res_consume` (the proportion of yield on a cell that is is consumed upon visit to the cell). Note that `consume_surv` is can still be used when `res_death_type > 0` (below), resulting in multiple potential sources of removal. Given `res_death_type = 0`, **user actions have no effect** on resource removal (to ensure that user actions do have an effect, set `res_death_type = 1` and `removal_pr = 0`; see below).
  1. *Density-independent removal*. Given this option, there is no density-dependent removal of resources within the resource sub-model. Resources are simply removed with a fixed probability of `removal_pr` (its default value is 0) each time the sub-model is run. This option should be used with great care because in the absence of density-dependence, it is possible for the population of resources to increase without limit and thereby greatly slow down simulation times. 
  2. *Density-dependent removal* (default). Given this option, removal of resources within the resource sub-model is caused entirely by density effects. The probability that a resource is removed is a function of the resource carrying capacity set using the `res_death_K` parameter. If the number of resources ($N$) is greater than `res_death_K` ($K$), then the probability that an individual resource is removed is defined by $(N - K) / N$. Removal then occurs independently for each resource based on this probability.
  3. *Density-independent and density-dependent removal*. This option allows a combination of both options (1) and (2), which affect removal independently. In other words, each resource is assigned a probability of removal `removal_pr` as in (1), and then independently assigned another probability of removal based on `res_death_K` as in (2). If removal occurs as a consequence of (1), (2), or both, then the resource is removed.

@@

>>>>

  0. *No explicit density independent or dependent removal, and no old age*. Given this option, the only way in resources can be removed is if users remove them through their actions (i.e., culling). Resources cannot die due to lack of resource consumption, density independent or dependent effects, or old age.
  1. *Density-independent removal*. Given this option, there is no explicit density-dependent removal of resources within the resource sub-model. Resources are simply removed with a fixed probability of `removal_pr` (its default value is 0) each time the sub-model is run. This option should be used with great care because in the absence of density-dependence, it is possible for the population of resources to increase without limit and thereby greatly slow down simulation times. Usually `res_death_type = 1` is most useful when combined with consumption limited survival (`consume_surv`) and reproduction (`consume_repr`); see below.
  2. *Density-dependent removal* (default). Given this option, removal of resources within the resource sub-model is caused by density effects. The probability that a resource is removed is a function of the resource carrying capacity set using the `res_death_K` parameter. If the number of resources ($N$) is greater than `res_death_K` ($K$), then the probability that an individual resource is removed is defined by $(N - K) / N$. Removal then occurs independently for each resource based on this probability.
  3. *Density-independent and density-dependent removal*. This option allows a combination of both options (1) and (2), which affect removal independently. In other words, each resource is assigned a probability of removal `removal_pr` as in (1), and then independently assigned another probability of removal based on `res_death_K` as in (2). If removal occurs as a consequence of (1), (2), or both, then the resource is removed.

Note that for all `res_death_type > 0`, removal can occur when the argument `consume_surv > 0` (its default value is 0). In this case, survival of a resource in a time step depends on that resource consuming at least `consume_surv` in yield on the landscape. In such cases, a natural carrying capacity can be generated as more resources result in higher total consumption. The amount of yield that a resource consumes is further affected by both `times_feeding` (how many times the resource moves and feeds on a new landscape cell during a time step) and `res_consume` (the proportion of yield on a cell that is is consumed upon visit to the cell). To ensure that resource death is *only* limited by consumption and user actions, set `res_death_type = 1` and `removal_pr = 0`. Under this scenario, resources will only die if the do not consume enough, are culled by users, or are above the `max_age`.

@@

**times_feeding**: By default, resources feed once at the start of each time step (`times_feeding = 1`), then move at the end the time step. Consequently, where they move to at the end of the time step will be where they feed at the start of the next time step, which gives users the opportunity to potentially cull or scare them prior to feeding. When `times_feeding > 1`, at the start of each time step, resource feeding on their cell, then immediately move to a new cell on which to feed. This feeding and moving continues until the resource has fed `times_feeding` times, at which point on the cell at which they last fed, potentially reproduce, then move again at the end of the time step. Feeding and moving actions happen in a random order for resources so that one resource does not do all of its feeding before another resource has any chance to feed. For example, if there are 10 resources and `times_feeding = 4`, then the 40 total feeding and moving actions happen in a random order.

### 2021-07-31 notebook/cran_vignettes/SI8.Rmd
Update the vignettes as necessary with changes mentioned in Issue #64 -- mostly typos, but also some small edits to the code that needed to be clarified

---
title: 'Adaptive timing of investment strategy'
subtitle: 'GMSE: an R package for generalised management strategy evaluation (New function vignette)'
author: | 
        | Adrian Bach&#xb9; &#xb2;
date: "[1] Biological and Environmental Sciences, University of Stirling, Stirling, UK [2] adrian.bach@stir.ac.uk"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
- \usepackage{lineno}
- \linenumbers
linestretch: 1
bibliography: gmse.bib
biblio-style: apalike
link-citations: true
linkcolor: blue
---

@@

And here the same simulation, exept managers update policy only when they observe the population to be plus or minus the target by 20%, and receive a bonus of 30% of their initial budget when they do not.

@@

Note how the costs plateau (lower left panel) when the population monitored (blue line in the upper left panel) is in between the two green dotted lines. Leaving the policy unchanged in these cases allowed managers to set the costs higher than the default maximum of 110 budget units. It also affects the number of cullings performed by users (lower right panel), which is more stable than when managers update policy every time step.

>>>>

---
title: 'Adaptive timing of investment strategy'
subtitle: 'GMSE: an R package for generalised management strategy evaluation (New function vignette)'
author: | 
        | Adrian Bach&#xb9; &#xb2;
date: "[1] Biological and Environmental Sciences, University of Stirling, Stirling, UK [2] adrian.bach@stir.ac.uk"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
- \usepackage{lineno}
linestretch: 1
bibliography: gmse.bib
biblio-style: apalike
link-citations: true
linkcolor: blue
---

@@

And here the same simulation, except managers update policy only when they observe the population to be plus or minus the target by 20%, and receive a bonus of 30% of their initial budget when they do not.

@@

Note how the costs plateau (lower left panel) when the population monitored (blue line, upper left panel) is in between the two green dotted lines. Leaving the policy unchanged in these cases allowed managers to set the costs higher than the default maximum of 110 budget units. It also affects the number of cullings performed by users (lower right panel), which is more stable than when managers update policy every time step.

### 2021-07-31 notebook/website_vignettes/SI5.Rmd
Update the vignettes as necessary with changes mentioned in Issue #64 -- mostly typos, but also some small edits to the code that needed to be clarified

```{r, fig.height = 5.2, fig.cap = "Output of the FLR plot function for an example Ricker model of stock recruitment on North Sea Herring data.", message = FALSE}
plot(newFL, cex = 0.7);
```

>>>>

```{r, fig.height = 5.2, fig.cap = "Output of the FLR plot function for an example Ricker model of stock recruitment on North Sea Herring data."}
plot(newFL, cex = 0.7);
```
